% SVN info for this file
\svnidlong
{$HeadURL$}
{$LastChangedDate$}
{$LastChangedRevision$}
{$LastChangedBy$}

% Remove header and footer
\thispagestyle{titlepage}

\begin{center}
  \newlength{\parSepLength}
  \setlength{\parSepLength}{10ex}

  \Large
  \centering

  % Main title
  \thinRule\par
  \par\vspace{0.15\parSepLength}
  \begin{minipage}{\textwidth}
    \centering
    \fontsize{40pt}{36pt}\selectfont\titleColor\scshape
    Mobile Application Projects\\
    
  \end{minipage}
  \par\vspace{0.25\parSepLength}
  \par\thinRule

  \vspace{0.125\parSepLength}

  \begin{minipage}{\textwidth}
    \centering
    \large
    CSE40333 - 01 \\
    CSE60333 - 01 \\
    Spring 2013\\
    
  \end{minipage}

  \vfill

  % Author
  \begin{minipage}{\textwidth}
    \centering
    \Large
    Nikhil Yadav and Salvador Aguinaga\\
    \{nyadav,saguinag\}@nd.edu
  \end{minipage}

  \vfill

  % Logo and other info
  \begin{minipage}{0.8\textwidth}
    \centering
    \small

    % Examiner
    \begin{minipage}[t]{0.45\textwidth}
%      \textsc{Examiner} \\
%      Prof. Examinus Person\\
%      Affiliation
	University of Notre Dame \\
	Department of Computer Science and Engineering\\
	
    \end{minipage}
    \hfill
    % Supervisor
    \begin{minipage}[t]{0.45\textwidth}
      \raggedleft
      \textsc{When:} M, W, F \\
      \textsc{Where:} Fitzpatrick 356A \\
      \textsc{Time:} 11:45A - 12:35P
    \end{minipage}
  \end{minipage}
\end{center}

\chapter{Syllabus}
\labelChapter{introduction}
\vspace{-16mm}
%\begin{table}[ht] 
%\begin{minipage}{0.49\textwidth}
%\centering\small\renewcommand*{\arraystretch}{1.5} 
%%\caption[]{Partial Database Table Structure}\label{tbl:dbstruc} 
%%%\begin{tabularx}{1\textwidth}{p{.2\textwidth}p{.25\textwidth} p{.475\textwidth}} % - 2\tabcolsep}
%%%\begin{tabular}{1\textwidth}{X|X|X|X|X|X|X}
%%%\begin{tabular}{c|c|c|c|c|c|c}
%%%\begin{tabular*}{\columnwidth}{@{\extracolsep{\stretch{1}}}*{7}{c}@{}}
%%%\begin{tabular*}{\columnwidth}{@{\extracolsep{\stretch{1}}}*{7}{c}@{}}
%%%-----------
%%\begin{tabularx}{1\textwidth}{X|X}
%%\begin{tabularx*}{1\textwidth}{p{.2\textwidth}p{.25\textwidth}} 
%%\hline
%%\begin{tabular}{\columnwidth}{@{\extracolsep{\stretch{1}}}*{2}{c}@{}}
%\begin{tabular}{l p{3.5in}}
%\textbf{Instructors:} & Nikhil Yadav and Salvador Aguinaga \\
%& Fitzpatrick 247 \\
%& \{nyadav,saguinag\}@nd.edu \\
%\textbf{Office Hours:} & Friday's lecture time slot: 11:45A - 12:35P\\
%\textbf{Pre-requisites:} & \\
%\textbf{Suggested Reference Books:} &   \\
%\textbf{Course Description:} & See inside.nd.edu class search \\
%\textbf{Course Objectives:} &   \\
%\textbf{Course Outline:} & \\
%\midrule
%\textbf{Dates:} & \textbf{Description} \\
%Jan 16 & Introduction, the syllabus, course
%		 requirements, and a review of computing platforms and SDKs \\
%Jan 18 & Hello world - iOS, Android, etc. \\
%Week 2 Jan 21 & 	\\
%Week 3 Jan 28 & 	\\
%Week 4 Feb 04 & 	\\
%Week 5 Feb 11 & 	\\
%
%\midrule
%%\textbf{Grade Policy:} & \\
%\textbf{Grading: }&	Attendance 5\%, Topic presentation 10\%, Mini-projects 15\%,
%				  	Midterm progress update 30\%, Final Project presentation 30\%,
%					and working source code submission 10\%  \\
%%\textbf{Homework} & \\
%\textbf{Attendance Policy }& University attendance policy applies\\
%\textbf{Academic Code of Honor} & \href{http://honorcode.nd.edu/the-honor-code/}{\textcolor{blue}{See this link:~\url{honorcode.nd.edu/the-honor-code/}}}\\
%\midrule
%\textbf{Important Dates }& \\
%Classes begin for Notre Dame & Jan 15 \\
%First class  & Jan 16 \\
%Mid-Term break & Mar 9 - Mar 17 \\
%Project Proposal & \\
%Midterm Progress Update & \\
%Final Project In-class Presentation & \\
%Finalists Project Presentation & \\
%\bottomrule
%
%
%
%
%
%\toprule 
%
%%% -----------
%%
%\end{tabular} 
%\end{minipage} 
%\end{table}

%\newpage
%% Tables
\begin{center}
\renewcommand*{\arraystretch}{1.5}
\begin{longtable}{ p{0.3\textwidth} p{0.6\textwidth} }
%\begin{longtable}{l *{2}{p{0.3\textwidth} } }
%\caption[Examples of sensors found in today's smartphones and typical manufacturers, in 
%	particular order]{Examples of sensors found in today's smartphones and typical 
%	manufacturers, in particular order} \label{tbl:sensors} \\

%\toprule[0.25mm] 
%\multicolumn{1}{l}{\textbf{}} & 
%\multicolumn{1}{l}{\textbf{}}   \\[1.0mm] %\toprule[0.25mm]
\endfirsthead

\multicolumn{2}{c}%
%{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
{{\bfseries \emph{-- continued from previous page}}} \\
\toprule[0.25mm] 
%\multicolumn{1}{l}{\textbf{Sensor}} &
%\multicolumn{1}{l }{\textbf{Sensor Manufacturers}}   \\\toprule[0.25mm] 
\endhead

\hline \multicolumn{2}{r}{{\bfseries \emph{Continued on next page...}}} \\
\endfoot

\bottomrule
\endlastfoot

\textbf{Instructors:} & Nikhil Yadav and Salvador Aguinaga \\
\textbf{Office Hours:} & Sal Tue/Thu 12p-1p, Nikhil Mon/Wed 2p-3p, and by appointment\\
& Location: Fitzpatrick Hall 212 \\
\textbf{Lecture Location:} & Fitzpatrick Hall 356A \\
\textbf{Lecture Date/Time:} & M W F 11:45A - 12:35P\\
\textbf{Websites:} & \href{http://www.nd.edu/~cse/2013sp/60333/}
{Course website: 
\textcolor{blue}{\url{http://www.nd.edu/~cse/2013sp/60333/}}}\\
				   & \href{http://darts.cse.nd.edu:8080/Plone/mobile-app-course/mobile-app-projects/}{Wiki: 
\textcolor{blue}{\url{http://darts.cse.nd.edu:8080/Plone/mobile-app-course/mobile-app-projects/}}}\\
\textbf{Course Description:} & \\
\multicolumn{2}{p{1\textwidth}}{\small This course will provide comprehensive project experience in development of mobile applications on two software platforms: iPhone OS and Android. Students will receive intensive tutorial introductions to each platform, covering hardware capabilities and limitations, the development environment, and the communications infrastructure available on campus to support networking. A few programming exercises will be assigned so that students can demonstrate basic development proficiency. The remainder of the course will be devoted to project work. Students will then develop project concepts. These concepts, along with others supplied by the instructors and other interested parties, will be assessed by teams of three students and one concept per team will be chosen for development. Development activity will include generation of design documentation, including specifications, UI mockups, state diagrams for execution and communications, presentations, and reports at various stages. During the development phase, teams will meet at least weekly with the instructors and with stakeholders acting as simulated "venture capitalists" funding the work. These meetings will involve a briefing of project status as well as demonstrations, interactions,etc. Each of these interactions will be graded. At the end of the semester, student projects will be evaluated by a jury and a suitable prize will be awarded to the project judged best in quality.} \\

\textbf{Pre-requisites:} & Department Approval Required; 
Must be enrolled in one of the following Major(s):
Computer Engineering (CPEG) ,  Computer Science (CS) ,  Computer Science \& Engineering (CSE) ,  Electrical Engineering (EE); Must have the following Classifications: Junior (03) ,  Senior (04) \\
\textbf{Course Outline:} & A detailed outline will be posted on the course website. Topics to be covered include:
  \begin{itemize} 
  \item Computing platforms and SDKs
  \item Review of Java and ObjectiveC programming
  \item Persistance: preferences, sqlite/CoreData, Parse, etc.
  \item Media: audio, video, images, plotting for data visualization
  \item Animation
  \item Multi-threading, responsiveness
  \item Location services
  \item Sensors 
  \item Touch, gestures, views (table-views, image-views, etc.)
  \end{itemize} \\

\textbf{Grading:} & The course grade will be based on: 
	\begin{itemize}
	\item Student topic presentation 10\%
	\item Mini-project/homework 20\%
	\item Project - functionality and design, midterm progress update, and 
	submission working source code 30\%
	\item Final project presentation and working source code 40\% 
	\end{itemize} 
	Class participation is encouraged: Contribute to the course by 
	providing coding tips, 	coding screenshots, source code snippets, and 
	mobile coding best practices examples via blog entries.  This type of 
	student participation will be considered for extra credit.\\
\textbf{Mini-projects} & Mini projects consist of programing and submitting
a working app of limited scope.  For example: an app that reads, parses and displays
an RSS feed. \\
\textbf{Attendance Policy }& Attendance is expected. Absences due to travel to conferences, job interviews, or due to a life-event must be 
communicated in person or via email prior to the expected absence\\

\textbf{Academic Code of Honor} & \href{http://honorcode.nd.edu/the-honor-code/}{\textcolor{blue}{~\url{honorcode.nd.edu/the-honor-code/}}}\\
\midrule
\textbf{Important Dates }	& \\
First day of class  			& Jan 16 \\
Student topic presentations 	& Starting Feb 25th \\
Project Proposal 			& Feb 08 \\
Midterm project report 		& Mar 08 \\
Mid-Term break 				& Mar 9 - Mar 17 \\
Final Project In-class 
Presentation 				& To be completed by May 1st\\
Finalists Project 
Presentation 				& On the scheduled final exam time-slot (TBD)\\
%\bottomrule


\end{longtable}
\end{center}%%\end{landscape}